Out-of-Sample Comparisons of Overfit Models

### 2013-12-19 paper.tex
Correct typo in mixignale proof
Rewrite assumption 3 - moments and smoothness
This commit changes the assumption on moments and
smoothness of the loss function (assumption 3) to
give the needed conditions for Lemma 1.

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous and has finite left and right
  derivatives almost everywhere.  Also, $L(0) = 0$, and there is a
  constant $B_L$ such that $\|D_t\|_\rho \leq B_L$ for all $t$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); $\| x_{it}' \hat{\theta}_{it} \|_2 \leq
  B_L$ and $\| x_{it}' \hat{\theta}_{it} \|_2 \leq B_L$; and
  \begin{equation*}
    \| L'(y_{t+h} - x_{it}'\tilde{\theta}_{it}) \|_2 \leq B_L
  \end{equation*}
  for $\tilde{\theta}_{it}$ a weighted average of any two estimates
  $\hat{\theta}_{it}$ and $\hat{\theta}_{it'}$.
\end{asmp}

@@

\vspace{\baselineskip}
\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} \clt s for
mixingale and \ned\ arrays will complete the proof.  Define
\[\label{eq:z1}
  Z_i = \ZDef
\]
where $b_T$ is a sequence that satisfies $b_T\leq P$,
$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
\citepos{Jon:97} Theorem 1 show that
\begin{equation*}
   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
\end{equation*}
and
\begin{equation*}
  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
  Z_i) + o_p(1).
\end{equation*}
Note that $\{Z_i - E_{R + (i-1)b_T},\mathcal{F}_{R + i b_T}\}_i$ is an
\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
long as
\begin{equation}\label{eq:cltvar2}
  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
\end{equation}
and
\begin{equation}\label{eq:cltvar1}
  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
    all $t \geq R$, so Hall and Heyde's condition (3.21) is
    unnecessary---see the remarks after their result.}
\end{equation}
Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
Lemma~\ref{lem:a2}. \qed

>>>>

\begin{asmp}\label{asmp-3}
  The loss function $L$ is continuous, has finite left and right
  derivatives almost everywhere, and $L(0) = 0$.  There is a constant
  $B_L$ and a function $L'$ that bounds the left and right derivative
  of $L$ such that $\|D_t\|_\rho \leq B_L$; $\|D_t^*\|_\rho \leq B_L$
  for all $t$, where
  \begin{equation*}
    D_t^* = L(y^* - x_1^{*\prime}\hat\theta_{1t})
    - L(y^* - x_2^{*\prime}\hat\theta_{2t})
  \end{equation*}
  and $(y^*, x_1^*, x_2^*)$ equals $(y_t, x_{1t}, x_{2t})$ in
  distribution but is independent of $\mathcal{F}_T$ ($\rho$ is defined
  in Assumption~\ref{asmp-1}); and
  \begin{equation*}
    \| L'(y^* - x_{i}^{*\prime}
    (\alpha \hat{\theta}_{iR} + (1-\alpha) \hat{\theta}_{iT})) \|_2
    \leq B_L
  \end{equation*}
  for any $\alpha \in [0,1]$.
\end{asmp}

@@

\vspace{\baselineskip}
\noindent\textit{Part 2.}  A modification of \citepos{Jon:97} \clt s for
mixingale and \ned\ arrays will complete the proof.  Define
\[\label{eq:z1}
  Z_i = \ZDef
\]
where $b_T$ is a sequence that satisfies $b_T\leq P$,
$b_T\to\infty$, and $b_T/P\to 0$.  The same arguments used in
\citepos{Jon:97} Theorem 1 show that
\begin{equation*}
   \SumOuterBlock{i} Z_i = P^{-1/2} \oosSum{s}{1} (D_t - \E_R D_t) + o_p(1).
\end{equation*}
and
\begin{equation*}
  \SumOuterBlock{i} Z_i = \SumOuterBlock{i} (Z_i - E_{R + (i-1)b_T}
  Z_i) + o_p(1).
\end{equation*}
Note that $\{Z_i - E_{R + (i-1)b_T} Z_i,\mathcal{F}_{R + i b_T}\}_i$ is an
\mds\ by construction, so \citepos{HaH:80} Theorem 3.2 and Corollary
3.1 ensure that $\sigma^{-1} \SumOuterBlock{i} Z_i \to^d N(0,1) $ as
long as
\begin{equation}\label{eq:cltvar2}
  \sigma^2 - \SumOuterBlock{i} \E_R Z_i^2 \to^p 0,
\end{equation}
and
\begin{equation}\label{eq:cltvar1}
  \SumOuterBlock{i} \E_R Z_i^2 - \SumOuterBlock{i} \ZSqCE \to^p 0.\footnote{Note that $\sigma^2 \in \mathcal{F}_t$ for
    all $t \geq R$, so Hall and Heyde's condition (3.21) is
    unnecessary---see the remarks after their result.}
\end{equation}
Equation (\ref{eq:cltvar2}) holds as in \citet{Jon:97} (see the proof
of his Theorem 2); (\ref{eq:cltvar1}) is ensured by
Lemma~\ref{lem:a2}. \qed
